---
title: "Lab 03 - Nobel laureates"
author: "Jonathan, Liam , griffin, micaela"
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

```{r chunk1, message = FALSE}
nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

26 variables, 935 columns
24,310 observations in the data set.
each row represents a diferent nobel laureate


### Exercise 2

#### Code

```{r nobel-living}
nobel_living <- filter(nobel, !is.na(country), gender != "org", is.na(died_date)) 
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 3

#### Code

```{r facet-bar-plot}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other"))

nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))

ggplot(nobel_living_science,
       mapping = aes(y = category)) +

geom_bar()+
  facet_grid(cols = vars(country_us))

```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*